---
title: "Lecture Assignment 11"
author: "Taiki Yamashita"
date: "2024-05-09"
output: pdf_document
---
```{r, echo=FALSE}
library("tidyverse")
```

# 11.3.5 1) 
# What are the most important arguments to locale()?
The local object has the arguments to set the following...
data and time formats: data_names, data_format, and time_format
time zone: tz
numbers: decimal_mark, grouping_mark
encoding: encoding


# 11.3.5 2)
# What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to “,”? What happens to the default value of decimal_mark when you set the grouping_mark to “.”?
locale will throw and error if the decimal and grouping marks are set to the same character...
locale(decimal_mark = ".", grouping_mark = ".") 
If the decimal_mark is set to the comma " ,", the grouping mark is set to the period "."...
```{r}
locale(decimal_mark = ",")
```
If the grouping mark is set to a period, the decimal mark is set to a comma...
```{r}
locale(grouping_mark = ".")
```

# 11.3.5 5)
# What’s the difference between read_csv() and read_csv2()?
The difference between read_csv() and read_csv2() is the delimiter. The read_csv() uses a comma, while the read_csv2() uses a semi-colon. Using the semi-colon is useful when commas are used as the decimal point. 


# 11.3.5 7)
# Generate the correct format string to parse each of the following dates and times:
```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"
```
The correct formats are...
```{r}
parse_date(d1, "%B %d, %Y")
parse_date(d2, "%Y-%b-%d")
parse_date(d3, "%d-%b-%Y")
parse_date(d4, "%B %d (%Y)")
parse_date(d5, "%m/%d/%y")
parse_time(t1, "%H%M")
```
time t2 uses real seconds...
```{r}
parse_time(t2, "%H:%M:%OS %p")
```




