---
title: "Lecture Assignment 4"
author: "Taiki Yamashita"
date: "2024-04-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(magrittr)
```

## 3.7.1 Exercises

## 1)
```{r, echo=F}
# The previous plot looked like this.
ggplot(data = diamonds) +
  stat_summary(
    mapping = aes(x = cut, y = depth),
    fun.min = min,
    fun.max = max,
    fun = median
  )
```

stat_summary is associated with geom_pointrange.
 
```{r}
ggplot(diamonds) +
  geom_pointrange(aes(cut, depth, min = depth, max = depth))
```

## 2)
geom_col leaves the data as it is. geom_bar() creates two variables which are count and prop, and then graphs the count data on the y-axis. With geom_col, you can plot the values of any x variable against any y variable.

```{r}
# An example of this would be plotting exactly x to y values.
aggregate.data.frame(diamonds$price, list(diamonds$cut), mean, na.rm = T) %>%
  print(.) %>%
  ggplot(aes(Group.1, x)) +
  geom_col()
```

## 3.8.1 Exercises

## 1)
```{r}
# This is the origninal plot given...
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

Although the 2 variables are continous, the chance of being in a single point is very discrete. On top of that, a lot of the points overlap. What we could do to fix this is to add a jitter.

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() +
  geom_jitter()
```

## 2)
The width and height control the amount of jittering.
```{r}
# To control the amount of jittering, you could add the width and the height.
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() +
  geom_jitter(width = 5, height = 10)
```

## 3.9.1 Exercises

## 1)
```{r}
ggplot(mpg, aes(factor(1), fill = factor(cyl))) +
  geom_bar(width = 1) +
  coord_polar(theta = 'y')
```

## 2)
What labs() would allow you to do is to control all the labels in the plot. An example of this would be...
```{r}
ggplot(mpg, aes(cyl, fill = as.factor(cyl))) +
    geom_bar() +
    labs(title = "This is a title!",
         subtitle = "This is a subtitle!",
         x = "This is the x-axis!",
         y = "This is the y-axis!",
         fill = "This is the fill!",
         caption = "This is a caption!")
```

