---
title: "Lecture Assignment 5"
author: "Taiki Yamashita"
date: "2024-04-18"
output: pdf_document
---

## 4.4 Exercises 1-3

## 1)
The reason why there is an error in the code is because the i in the second my_variable is not actually an i. A fixed version of the code should look like this...
```{r}
my_variable <- 10
my_variable
```

## 2) 
Here is the modified and correct version of the original code provided.
```{r}
library(tidyverse)

ggplot(data = mpg) + # dota to data
  geom_point(mapping = aes(x = displ, y = hwy))
filter(mpg, cyl == 8) # fliter to filter and cyl = 8 to cyl == 8
filter(diamonds, carat > 3) # diamond to diamonds
```

## 3)
What I see are all the different keyboard shortcuts you can use in the studio.  
To navigate to the same screen, click on "Tools" at the top, then click on "Keyboard Shortcuts Help".

## 11.2.2 Exercises 1-3

## 1)
You would use the read_delim() function with the argument delim = "|". It would look something like this...
```{r}
read_delim("a|b|c\n1|2|3\n4|5|6", delim = "|")
```


## 2)
All of the arguments. This is because both the functions read_csv() and read_tsv() use read_delim as the function doing the work. Both functions just call read_delim with a set of predefined options for csv and tsv formats using tokenize_* functions. The tokenize_* functions simply returns a list with the characteristics of each format.

## 3)
The most important argument is col_positions which defines the column positions. We use col_positions to determine the width at which each column is separated. You can determine the width with the fwf_* helper functions. 

