---
title: "Lecture Assignment 9"
author: "Taiki Yamashita"
date: "2024-05-02"
output: pdf_document
---

```{r, echo = FALSE}
library("tidyverse")
library("nycflights13")
library("ggbeeswarm")
library("lvplot")
library("ggstance")
```

# 7.5.1.1 1) 
# Use what you’ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights.

What we can do is instead of using a freqplot is that we can now use a box plot!
```{r}
nycflights13::flights %>%
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>%
  ggplot() + 
  geom_boxplot(mapping = aes(y = sched_dep_time, x = cancelled))
```

# 7.5.2.1 3)
# Why is it slightly better to use aes(x = color, y = cut) rather than aes(x = cut, y = color) in the example above?

Usually it's better to use the categorical variable with a larger number of categories or the longer labels on the y axis. But, switching the order will not result in overlapping labels. Labels should be horizontal because it is easier to read.

```{r}
diamonds %>%
  count(color, cut) %>%
  ggplot(mapping = aes(y = color, x = cut)) +
  geom_tile(mapping = aes(fill = n))
```

# 7.5.3.1 2) 
# Visualise the distribution of carat, partitioned by price.
A graph of a box plot with 10 bins an equal number of observations. The width is determined by the number of observations.
```{r}
ggplot(diamonds, aes(x = cut_number(price, 10), y = carat)) + 
  geom_boxplot() +
  coord_flip() + 
  xlab("Price")
```
Another visualization would be a box plot with 10 equal-width bins of 2000 dollars. boundary = 0 is what ensures that the first bin is 0 to 2000 dollars.
```{r}
ggplot(diamonds, aes(x = cut_width(price, 2000, boundary = 0), y = carat)) + 
  geom_boxplot(varwidth = TRUE) + 
  coord_flip() + 
  xlab("Price")
```

# 7.5.3.1 3)
# How does the price distribution of very large diamonds compare to small diamonds? Is it as you expect, or does it surprise you?

```{r}
diamonds %>%
  filter(between(carat, 0, 2.5)) %>%
  mutate(carat = cut_width(carat, 1)) %>%
  ggplot(aes(price)) +
  geom_histogram() +
  facet_wrap(~ carat)
```
This was very surprising as I was expecting very little variance. It seems as though big diamonds can cost anything between 5000 and 18000. Whereas small ones have very little variance. 

# 7.5.3.1 5)
# Two dimensional plots reveal outliers that are not visible in one dimensional plots. For example, some points in the plot below have an unusual combination of x and y values, which makes the points outliers even though their x and y values appear normal when examined separately.

```{r}
ggplot(data = diamonds) + 
  geom_point(mapping = aes(x=x, y=y)) +
  coord_cartesian(xlim = c(4, 11), ylim = c(4, 11))
```
There is a strong relationship between x and y. The outliers are not as extreme in either x or y. A binned plot would not reveal these outliers, and may lead us to conclude that the largest value of x was an outlier even thogh it appears to fit the bivariate pattern well. 
